Application of the XT3D Multi-Point Flux Approximation to Vertically Staggered Grids in MODFLOW 6 to Improve Accuracy of Simulated Flows in Steeply Dipping Layers

### 2022-09-20 latex/article.tex
* Substantial additions/changes to the disu_approach notebook, mostly to add the option to include the "domain" surrounding the channel, plus other refactoring and tweaks. * Minor updates to the manuscript.  Note that the naming convention for the figures from the scenario runs has changed.

To simulate flow along a channel inclined at angle $\theta$, heads are specified at the centers of cells along the perimeter of the model using an analytical solution that corresponds to a unit head gradient inclined at angle $\theta$ \citep{bardot2022}:

@@

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-s-nocc-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-nocc-head}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-x-nocc-head.png}
	\caption{XT3D}
	\label{fig:disu-x-nocc-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically offset grid. The news is all bad; XT3D doesn't really help. (disu\_approach model, 5x11 grid without cross-connections, $30^{\circ}$ incline, set up for flow along the channel)}
\label{fig:figures}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-s-nocc-cf-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-nocc-cf-head.}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-x-nocc-cf-head.png}
	\caption{XT3D}
	\label{fig:disu-x-nocc-cf-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically offset grid and boundary heads set up for crossflow. The standard formulation is a fail, but XT3D nails it, even without cross-connections. (disu\_approach model, 5x11 grid without cross-connections, $30^{\circ}$ incline, set up for flow across the channel)}
\label{fig:figures}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-s-cc-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-cc-head}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-x-cc-head.png}
	\caption{XT3D}
	\label{fig:disu-x-cc-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically staggered grid with cross-connections. The news is much better; the standard formulation isn't horrible, and XT3D nails it. (disu\_approach model, 5x11 grid with cross-connections, $30^{\circ}$ incline, set up for flow along the channel)}
\label{fig:figures}
\end{figure}

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-s-cc-cf-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-cc-cf-head}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-x-cc-cf-head.png}
	\caption{XT3D}
	\label{fig:disu-x-cc-cf-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically staggered grid with cross-connections and boundary heads set up for crossflow. The standard formulation does pretty well, and XT3D nails it again. (disu\_approach model, 5x11 grid with cross-connections, $30^{\circ}$ incline, set up for flow across the channel)}
\label{fig:figures}
\end{figure}

@@

>>>>

To simulate flow along a channel inclined at angle $\theta$, heads are specified at the centers of cells along the perimeter of the model (XXXXX this assumes we're using the transect\_benchmark version of the model, which includes the "domain," for all of our final runs XXXXX) using an analytical solution that corresponds to a unit head gradient inclined at angle $\theta$ \citep{bardot2022}:

@@

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-af-vo-s-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-nocc-head}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-af-vo-x-head.png}
	\caption{XT3D}
	\label{fig:disu-x-nocc-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically offset grid. The news is all bad; XT3D doesn't really help. (preliminary result from disu\_approach model, 5x11 grid without cross-connections, $30^{\circ}$ incline, set up for flow along the channel)}
\label{fig:figures}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-cf-vo-s-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-nocc-cf-head.}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-cf-vo-x-head.png}
	\caption{XT3D}
	\label{fig:disu-x-nocc-cf-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically offset grid and boundary heads set up for crossflow. The standard formulation is a fail, but XT3D nails it, even without cross-connections. (preliminary result from disu\_approach model, 5x11 grid without cross-connections, $30^{\circ}$ incline, set up for flow across the channel)}
\label{fig:figures}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-af-vs-s-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-cc-head}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-af-vs-x-head.png}
	\caption{XT3D}
	\label{fig:disu-x-cc-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically staggered grid with cross-connections. The news is much better; the standard formulation isn't horrible, and XT3D nails it. (preliminary result from disu\_approach model, 5x11 grid with cross-connections, $30^{\circ}$ incline, set up for flow along the channel)}
\label{fig:figures}
\end{figure}

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-cf-vs-s-head.png}
	\caption{standard conductance-based formulation}
	\label{fig:disu-s-cc-cf-head}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\textwidth}
	\includegraphics[width=\textwidth]{../figures/disu-cf-vs-x-head.png}
	\caption{XT3D}
	\label{fig:disu-x-cc-cf-head}
\end{subfigure}
\caption{Specific discharge and head for a vertically staggered grid with cross-connections and boundary heads set up for crossflow. The standard formulation does pretty well, and XT3D nails it again. (preliminary result from disu\_approach model, 5x11 grid with cross-connections, $30^{\circ}$ incline, set up for flow across the channel)}
\label{fig:figures}
\end{figure}

@@

\subsection{Domain}
Results with the surrounding "domain" (from an updated disu\_approach notebook) are similar but not identical, apparently due to the "staircase" effect. Might be best to presnt most of our results without the domain, at least when illustrating the main problem and its solution (to keep the "theory" clear), then discuss what happens when the domain is present (which is more like in practice).
